tl20-05_berghei_pir_DESEQ

### 2021-09-17 chapter3_results_bergheiPir/Manuscript_berghei_pir_DESEQ.Rmd
Save deseq heatmap and fix remove asex.mix v ring comp

```{r}
ordered_stages <- ordering(unique(coldata$stage), order_vector = r_order_vector)
comparisons <- c(
  lapply(seq_along(ordered_stages),
         function(i){ if(i < length(ordered_stages)){ c(ordered_stages[i],ordered_stages[i+1]) } }
  ),
  list(
    c('Liv.post48h','Liv.24h'),
    c('Asex.Schiz','Gam.Male'),
    c('Ook','Sporoz'),
    c('Gam.Male','Asex.Mixed'),
    c('Gam.Male','Liv.Meroz')
  )
)
comparisons <- comparisons[-which(sapply(comparisons, is.null))]
#Remove some comparisons
comparisons <- comparisons[!grepl(comparisons, pattern = 'Asex\\.Mixed-Asex\\.Ring')]

@@

sig_pirs %>% filter(Geneid %in% 'PBANKA_0600031')

Heatmap(sig_pirs_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        # rect_gp = gpar(col = "white", lwd = 1),
        border_gp = gpar(col = "black", lty = 1),
        na_col = 'white',
        show_column_names = FALSE,
        column_split = gsub(pir_clade$clade[match(colnames(sig_pirs_cast), pir_clade$Geneid)],
                            pattern = 'ancestral',
                            replacement = 'a')
        )

>>>>

```{r}
ordered_stages <- ordering(unique(coldata$stage), order_vector = r_order_vector)
comparisons <- c(
  lapply(seq_along(ordered_stages),
         function(i){ if(i < length(ordered_stages)){ c(ordered_stages[i],ordered_stages[i+1]) } }
  ),
  list(
    c('Liv.post48h','Liv.24h'),
    c('Asex.Schiz','Gam.Male'),
    c('Ook','Sporoz'),
    c('Gam.Male','Asex.Mixed'),
    c('Gam.Male','Liv.Meroz')
  )
)
comparisons <- comparisons[-which(sapply(comparisons, is.null))]
#Remove some comparisons
comparisons <- comparisons[!(grepl(comparisons, pattern = 'Asex\\.Mixed') & grepl(comparisons, pattern = 'Asex\\.Ring'))]

@@

sig_pirs %>% filter(Geneid %in% 'PBANKA_0317181')
sig_pirs %>% filter(Geneid %in% 'PBANKA_0600031')

png(filename = "plots/thesis_chapter3_figure_statsCompHeatmap_inidvidualGenes.png",
    width = 7,
    height = 5,
    units = "in",
    res = 330)
Heatmap(sig_pirs_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        # rect_gp = gpar(col = "white", lwd = 1),
        border_gp = gpar(col = "black", lty = 1),
        na_col = 'white',
        show_column_names = FALSE,
        column_split = gsub(pir_clade$clade[match(colnames(sig_pirs_cast), pir_clade$Geneid)],
                            pattern = 'ancestral',
                            replacement = 'a')
)
dev.off()
```
